Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-07-17 manuscript.Rmd
Working on growth models.

articles.df <- left_join(n.so, n.yr) %>%
    group_by(year) %>%
    summarize(N = n()) %>%
    mutate(year = as.numeric(year), CumSum = cumsum(N)) %>%
    ungroup() %>%
    arrange(desc(N), year) %>%
    rename(Year = year)

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

>>>>

articles.df <- left_join(n.so, n.yr) %>%
    group_by(year) %>%
    summarize(N = n()) %>%
    mutate(year = as.numeric(year), CumSum = cumsum(N)) %>%
    ungroup() %>%
    arrange(year) %>%
    rename(Year = year)

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

exp.07 <- c(737, rep(NA, 24)) 
for(i in 2:25){
    exp.07[i] <- exp.07[i-1] + exp.07[i-1]*.05
}

exp.175 <- c(737, rep(NA, 24))
for(i in 2:25){
       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
    }

articles.df$exp.175 <- exp.175
articles.df$exp.07  <- exp.07

ggplot(articles.df, aes(Year, CumSum, group =1)) + 
    theme_bw() + 
    geom_point(colour=cp[2], size = 3, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    #scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(Year, exp.07), colour = cp[4]) +
    geom_line(aes(Year, exp.175), colour = cp[3]) +
    geom_smooth(method = "lm", colour = cp[1])

tail(articles.df)

head(articles.df)

exp.175 <- c(737, rep(NA, 24))

for(i in 2:25){
       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
 }

articles.df$exp.175 <- exp.175

```{r, eval=FALSE}
articles.df$YearRecode <- c(nrow(articles.df):1)
ggplot(articles.df, aes(Year, N)) +  
  geom_smooth(method="lm") + 
  geom_line() +
  geom_point()

options(digits = 4)
x <- lm(N ~ YearRecode, data = articles.df)
summary(x)

articlesN <- rev(articles.df$N)
articlesN <- ts(articlesN, frequency=1, start = 1989, end = 2013)
diff(articlesN)/articlesN[-nrow(articlesN),]*100

curr <- articles.df$N[-1]
prev <- articles.df$N[1:(length(articles.df$N)-1)]
articles.df <- arrange(articles.df, Year)
articles.df$monChange <- c(0, (100 *  (curr-prev) / prev)) 
articles.df <- mutate(articles.df, positiveNegative = as.factor(ifelse(articles.df$monChange >= 0, "Positive", "Negative")))

ggplot(articles.df, aes(Year, monChange, fill = positiveNegative)) + geom_bar(stat="identity") 
mean(articles.df$monChange[2:25])
